\documentclass{article}
\linespread{1.3}
\usepackage[margin=50pt]{geometry}
\usepackage{amsmath, amsthm, amssymb, amsthm, tikz, fancyhdr, float, graphicx, spverbatim, systeme}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\changefont}{\fontsize{15}{15}\selectfont}

\fancypagestyle{firstpageheader}{
  \fancyhead[R]{
    \changefont
    \parbox[t]{4cm}{ % Adjust width as needed
      Michael Huang\\
      EN.555.644.81\\
      Homework 8
    }
  }
}

\begin{document}

\thispagestyle{firstpageheader}
{\Large 

\section*{11.12}
The price of a non-dividend paying stock is \$19 and the price of a three-month European call option on the stock with a strike price of \$20 is \$1. The risk-free rate is 4\% per annum. What
is the price of a three-month European put option with a strike price of \$20? \\ \\
According to put-call parity:
\[
  c + D + Ke^{(-rT)} = p + S_0
\]
\[
  1 + 0 + 20e^{(-0.04 \cdot \frac{3}{12})} = p + 19
\]
\[
  p = 1 + 20e^{-0.01} - 19
\]
\[
  p = 20 \cdot 0.99004983374 - 18 = 19.8009966748 - 18 = 1.8009966748 \approx \boxed{\textbf{\$1.80}}
\]


}
{\Large 

\section*{11.19}
The price of a European call that expires in six months and has a strike price of \$30 is \$2. The underlying stock price is \$29, and a dividend of \$0.50 is expected in two months and again in five months. Interest rates (all maturities) are 10\%. What is the price of a European put option that expires in six months and has a strike price of \$30?
\[
  c + D + Ke^{(-rT)} = p + S_0
\]
\[
  2 + 0.50(e^{-0.10 \cdot \frac{2}{12}} + e^{-0.10 \cdot \frac{5}{12}}) + 30e^{(-0.10 \cdot \frac{6}{12})} = p + 29
\]
\[
  p = 2 + 0.50(0.98347145382 + 0.95918945711) + 30e^{-0.05 } - 29
\]
\[
  p = 2 + 0.97133045546 + 28.536882735 - 29
\]
\[
  p = 2.50821319046 \approx \boxed{\textbf{\$2.51}}
\]

}
{\Large 

\section*{11.20}
Explain the arbitrage opportunities in Problem 11.19 if the European put price is \$3. \\ \\
We found in Problem 11.19 that the fair put price should be \$2.51, so if this price is actually \$3, then there is an arbitrage opportunity with the put being overpriced and the call being underpriced. We can therefore \boxed{\textbf{short both the put and underlying stock}}, and then also \boxed{\textbf{buy the call}}. We first immediately make -2 + 3 + 29 = \$30, and we would then profit in the corresponding scenarios for the final stock price: \\
- If the stock price is above \$30, we exercise the call option and buy the stock for \$30, or with PV \(30e^{-0.10 \cdot \frac{6}{12}} = 30 \cdot 0.9512294245 = 28.536882735 \approx 28.54\), and the dividends on the short cost \(0.50(e^{-0.10 \cdot \frac{2}{12}} + e^{-0.10 \cdot \frac{5}{12}}) = 0.50(0.98347145382 + 0.95918945711) = 0.97133045546 \approx 0.97\), so we end up with a PV-adjusted profit of 30 - 28.54 - 0.97 = \$0.49, which is exactly the difference in the put price. \\
- If the stock price is below \$30, the put we shorted is exercised, so we are still forced to buy the stock for \$30, with the same PV calculation of before as 28.54. We still are short the stock, so we pay the same 0.97 dividend as before. The profit is therefore the same \$0.49 as before. 

}
{\Large 

\section*{11.23}
Prove the result in equation (11.7). (Hint: For the first part of the relationship consider (a) a portfolio consisting of a European call plus an amount of cash equal toK and (b) a portfolio consisting of an American put option plus one share.) \\ \\


}
{\Large 

\section*{11.24}
Prove the result in equation (11.11). (Hint: For the first part of the relationship consider (a) a portfolio consisting of a European call plus an amount of cash equal toD K+ and (b) a portfolio consisting of an American put option plus one share.) \\ \\


}
{\Large 

\section*{11.26}
Use the software DerivaGem to verify that Figures 11.1 and 11.2 are correct. 


}
{\Large 

\section*{11.31}
Suppose that \(c_1, c_2,\) and \(c_3\) are the prices of European call options with strike prices \(K_1, K_2,\) and \(K_3\), respectively, where \(K_3 > K_2 > K_1\) and \(K_3 - K_2 = K_2 - K_1\). All options have the same maturity. Show that 
\[
  c_2 \leq 0.5(c_1 + c_3)
\]
(Hint: Consider a portfolio that is long one option with strike price \(K_1\), long one option with strike price \(K_3\), and short two optiosn with strike price \(K_2\).) \\ \\


}
{\Large 

\section*{.}
Consider an option on a stock when the stock price is \$41, the strike price of \$40, the risk-free rate is 6\%, the volatility is 35\%,and the time to maturity is 1 year. Assume that a dividend of \$0.50 is expected after six months. 

\subsection*{(a)} 
Use DerivaGem to value the option assuming it is a European call. \\ \\

\subsection*{(b)}
Use DerivaGem to value the option assuming it is a European put. \\ \\

\subsection*{(c)}
Verify that put-call parity holds. \\ \\

\subsection*{(d)}
Explore using DerivaGem what happens to the price of the options as the time to maturity becomes very large and there are no dividends. Explain your results. \\ \\

}

\end{document}